Toxic code snippets on Stack Overflow

### 2017-11-07 cloverflow-tse/cloverflow.tex
Small fixes to the TSE paper:
1) address the threat to validity of selecting only accepted answers.
2) modify RQ2 to "how" question instead of "why".

We performed an empirical study of online code clones between Stack
Overflow and 111 Java open source projects to answer the following
research questions:
\begin{itemize}
	\item \textbf{RQ1 (Online code clones): }\textit{To what extent is source
		code cloned between Stack Overflow and open source projects?} We
	quantitatively measured the number of online code clones between Stack
	Overflow and open source projects to understand the scale of the
	problem. 
	\item \textbf{RQ2 (Patterns of online code clones): }\textit{Why do online
		code clones occur?} We categorised online clones into seven
	categories allowing insights to why online code clones are created.
	\item \textbf{RQ3 (Outdated online code clones): }\textit{Are
		online code clones up-to-date compared to their counterparts in the
		original projects?} We were interested in the outdated Stack
	Overflow code examples since users are potentially reusing
	them. 
	\item \textbf{RQ4 (Software licensing violation): }\textit{How often do
		licensing conflicts occur between Stack Overflow clones and their
		originals?} We investigated whether the reuse of online code clones
	can cause software developers to violate licenses.
	\item \textbf{RQ5 (Stack Overflow answerers' awareness): }

@@

\subsection{RQ2: Patterns of Online Code Cloning}
\vspace{0.25cm}
\textit{Why do online code clones occur?}
\vspace{0.25cm}

@@

\textbf{Internal validity:} 
We applied
different mechanisms to ensure the validity of the clone
pairs we classified.  First, we used two widely-used
clone detection tools, Simian and SourcererCC.  We tried five other
clone detectors but could not add them to the study due to their
scalability issues and susceptibility to incomplete code snippets.
We adopted Bellon's agreement metric~\cite{Bellon2007}
to merge clone pairs for the manual
classification and avoid double counting of the same clone pairs. 
Nevertheless, our study might still suffer from false negatives, i.e.~online 
code clones that are not reported by the tools or are filtered 
out by the size (less than 10 lines) within the clone detection process.
% We also
% applied the Bellon's clone agreement to 4 different combinations of
% the tools' configurations.  For disagreed clone pairs, we applied
% several filters to remove spurious and uninteresting clones.

>>>>

We performed an empirical study of online code clones between Stack
Overflow and 111 Java open source projects to answer the following
research questions:
\begin{itemize}
	\item \textbf{RQ1 (Online code clones): }\textit{To what extent is source
		code cloned between Stack Overflow and open source projects?} We
	quantitatively measured the number of online code clones between Stack
	Overflow and open source projects to understand the scale of the
	problem. 
	\item \textbf{RQ2 (Patterns of online code clones): }\textit{How do online
		code clones occur?} We categorised online clones into seven
	categories allowing insights to how online code clones are created.
	\item \textbf{RQ3 (Outdated online code clones): }\textit{Are
		online code clones up-to-date compared to their counterparts in the
		original projects?} We were interested in the outdated Stack
	Overflow code examples since users are potentially reusing
	them. 
	\item \textbf{RQ4 (Software licensing violation): }\textit{How often do
		licensing conflicts occur between Stack Overflow clones and their
		originals?} We investigated whether the reuse of online code clones
	can cause software developers to violate licenses.
	\item \textbf{RQ5 (Stack Overflow answerers' awareness): }

@@

\subsection{RQ2: Patterns of Online Code Cloning}
\vspace{0.25cm}
\textit{How do online code clones occur?}
\vspace{0.25cm}

@@

\textbf{Internal validity:} 
We applied different mechanisms to ensure the validity of the clone pairs we
classified.  First, we used two widely-used clone detection tools, Simian and
SourcererCC.  We tried five other clone detectors but could not add them to the
study due to their scalability issues and susceptibility to incomplete code
snippets. We adopted Bellon's agreement metric~\cite{Bellon2007} to merge clone
pairs for the manual classification and avoid double counting of the same clone
pairs. Nevertheless, our study might still suffer from false negatives,
i.e.~online code clones that are not reported by the tools or are filtered out
by the size (less than 10 lines) within the clone detection process. We selected
Stack Overflow accepted answers in this study to focus on code snippets that
solve problems in the question and are often showed on top of the answer list.
While most of the time they are also the highest voted answers, there is some
time that they are not. We plan to incorporate the highest voted answers in the
future work.
% We also
% applied the Bellon's clone agreement to 4 different combinations of
% the tools' configurations.  For disagreed clone pairs, we applied
% several filters to remove spurious and uninteresting clones.
